Methods paper for erosion

### 2018-01-08 docs/methods/erosion_methods.tex
Doing convergence test for shape and putting in methods paper.
NM
Put convergence test in methods paper
started the introduction

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Erosion by flowing fluid plays an essential role in diverse processes.
Many of the flows are geophysical, such as the formation of sand dunes
or erosion due to groundwater flow.  In both these examples, there is a
feedback process between the flow and the erodible body.  In particular,
the shape of the eroding body affects the flow, while the flow changes
the shape of the eroding body.

\paragraph{Contributions} The present study will develop numerical
methods to simulate viscous erosion of a multiply-connected
two-dimensional geometry.  By assuming the flow is viscous, we are
assuming the flow is very slow, such as in groundwater flow.  Moreover,
by allowing for complex multiply-connected domains, the erosion caused
by the non-local complex interactions between different bodies is
modeled.

@@

\paragraph{Related work}

\paragraph{Outline of the paper}

This is a methods paper
\begin{itemize}
  \item Boundary integral equation formulation
  \item How we compute the shear stress and pressure
  \item Multiple bodies
  \item Avoiding stokes paradox
  \item {\thL} formulation
  \item Regularization
\end{itemize}

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
\caption{50 bodies with vorticity}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated using 50circ128.in with epsfac = 10, sigfac = 10, dt = 2e-4, fixpdrop = 1.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Erosion by flowing fluid plays an essential role in diverse processes.
Many of the flows are geophysical, such as the formation of sand dunes
or erosion due to groundwater flow.  In both these examples, there is a
feedback process between the flow and the erodible body.  In particular,
the shape of the eroding body affects the flow, while the flow changes
the shape of the eroding body.  This fluid-mechanical feedback
system has be simulated in idealized cases such as a single eroding body
in a uniform flow~\cite{moo-ris-chi-zha-she2013}.  To further develop
insight into the effect of two-dimensional erosion, we consider erosion
of a multiply-connected domain (Figure~\ref{fig:50bodies}), such as a
porous media that is typically used to model groundwater flow.

Because of the scales involved with groundwater flow, we will restrict
our attention to Stokesian dynamics.  That is, the fluid equations will
be governed by the incompressible Stokes equations.  Because of the
linearity of the underlying equations, a boundary integral equation is
well-suited as it can resolve complex geometries, the interactions
between bodies, all the while achieving high-order accuracy and
computational efficiency.

\paragraph{Contributions} The present study will develop numerical
methods to simulate viscous erosion of a multiply-connected
two-dimensional geometry.  By assuming the flow is viscous, we are
assuming the flow is very slow and in small length scales, as is the
case in groundwater flow.  Moreover, by allowing for complex
multiply-connected domains, the erosion caused by the non-local complex
interactions between different bodies is modeled.

@@

\paragraph{Related work}
Simulating eroding bodies has been studied analytically, experimentally,
and numerically.  Because of the scales involves with geophysical flows,
most of these works consider high Reynolds number flows.  For instance,
the experimental work of Moore et al.~\cite{moo-ris-chi-zha-she2013}
considers on the order of $10^4$.  For low Reynolds number flows,
Mitchell and Spagnolie~\cite{Mitchell2016} simulate the erosion of a
mobile body in three dimensions, but they only consider single body.

To simulate multiple bodies, it is essential to resolve the nonlocal
effects between the different bodies.  In this work, these interactions
are included with high-order accuracy by using an integral equation
method.  Integral equations have been used extensively to simulate
viscous fluids in complex geometries.  One particular application are
particulate flows, such as bubbles or droplets, and the classic book of
Pozrikidis~\cite{poz1992} describes boundary integral formulations for
such problems.

\paragraph{Outline of the paper}
In Section~\ref{s:formulation}, we describe the governing equations for
both the fluid and describe the erosion model using a \thL framework.
In Section~\ref{s:method}, the numerical methods in both space and time
are described.  Section~\ref{s:results} gives several numerical
examples.  Finally, concluding remarks are made in
Section~\ref{s:conclusions}

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
\caption{\label{fig:50bodies} 50 bodies with vorticity}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated using 50circ128.in with epsfac = 10, sigfac = 10, dt = 2e-4, fixpdrop = 1.

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is 56\% of the vanishing time.
} 
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{c l l}
\hline
\hspace{0.5pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order \\
\hline
1/100	& 4.69E-6		& --		\\
1/200	& 1.26E-6		& 1.90	\\
1/400	& 3.26E-7		& 1.95	\\
1/800	& 8.28E-8		& 1.98	\\
1/1600	& 2.09E-8		& 1.99	\\
1/3200	& 5.26E-9		& 1.99	\\
1/6400	& --			& --		\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
